Boundary Labeling for annotated documents

### 2017-10-28 LaTeX/Paper.tex
Paper: Minor corrections. Program: No changes.

A \emph{Graph} $G=\langle V, E \rangle$ is a tuple of \emph{Vertices} $(V=\{v_1, v_2, ..., v_n\})$ and \emph{Edges} $(E=\{e_1, e_2, ..., e_m\})$. A vertex $v_i (i~\in~\mathbb{N})$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e_i \, (i~\in~\mathbb{N})$ is a relation between two vertices $(E:V\rightarrow  V\times V)$. The vertices forming the edge are considered \emph{adjacent} to each other. Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
 A \emph{Path} $(P=v_1, ..., v_h)$ is an ordered series of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v_s \in V$ and explores the graph by traversing its edges as far as possible before backtracking. In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{Polylines} are a connected series of \emph{Line segments}. Line segments are straight lines that contain each point between their starting and end point. %Open vs. closed line segments?
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is an area designated to hold labels and is located off to a side so the labels don't obscure anything.
The point or object that this information refers to is called a \emph{Site}. The site and the label are connected via a \emph{Leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the leader from Fig~\ref{fig:term} would be classified as an OPO-Leader.
The location where a leader connects to the label is called the \emph{Port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

>>>>

A \emph{graph} $G=\langle V, E \rangle$ is a tuple of \emph{vertices} $V=\{v_1, v_2, ..., v_n\}$ and \emph{edges} $E=\{e_1, e_2, ..., e_m\}$. A vertex $v$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e$ is a relation between two vertices $E:V\rightarrow  V\times V$. %Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
We call two vertices $u,v \in V$ \emph{adjacent}, if the edge $e=(u,v) \in E$.
 A \emph{path} $P=v_1, ..., v_h$ is an ordered series of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v \in V$ and explores the graph by traversing its edges as far as possible before backtracking. In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{polylines} are a connected series of \emph{Line segments}. Line segments are straight lines that contain each point between their starting and end point. %Open vs. closed line segments?
\emph{labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is an area designated to hold labels and is located off to a side so the labels don't obscure anything.
The point or object that this information refers to is called a \emph{site}. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the leader from Fig~\ref{fig:term} would be classified as an OPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity
